---
title: "UKB Current Depression Phenotype at Imaging"
author: "Hannah Casey"
date: "2025-02-26"
output: html_document
---
```{r setup}
library(dplyr)
```


## Load in touchscreen questionnaire data
```{r Get data}
UKB_touchscreen <- readRDS("/Volumes/GenScotDepression/data/ukb/phenotypes/fields/2021-04-phenotypes-ukb44797/Touchscreen.rds")
```

## Get required variables to derived lifetime depression - based on Smith et al phenotypes:https://biobank.ndph.ox.ac.uk/showcase/refer.cgi?id=158772
```{r get lifetime depression varaibles}

UKB_touchscreen_lifetime_dep <- UKB_touchscreen %>%
  select(f.eid, f.4598.2.0, f.4609.2.0, f.4620.2.0, f.4631.2.0, 
         f.5375.2.0, f.5386.2.0, f.2090.2.0, f.2100.2.0) 
```

## Derive lifetime depression phenotypes
```{r derive Smith et al depression phenotypes}
# (1) Ever felt depressed for a whole week - 4598
# (2) Ever disinterested or unenthusiastic for a whole week - 4631
# (3) Only 1 episode - 4620
# (4) ≥ 2 episodes - 4620
# (5) Episode lasted ≥ 2 weeks - 4609
# (6) Ever seen a GP for nerves, anxiety, tension or depression. - 2090
# (7) Ever seen a psychiatrist for nerves, anxiety, tension or depression - 2100

UKB_touchscreen_lifetime_dep$depressed_week <- recode(
  UKB_touchscreen_lifetime_dep$f.4598.2.0,
  "No" = 0,
  "Yes" = 1
)

UKB_touchscreen_lifetime_dep$disinterested_week <- recode(
  UKB_touchscreen_lifetime_dep$f.4631.2.0,
  "No" = 0,
  "Yes" = 1
)

UKB_touchscreen_lifetime_dep$only_one <- NA
UKB_touchscreen_lifetime_dep$only_one[UKB_touchscreen_lifetime_dep$f.4620.2.0 == 0 | UKB_touchscreen_lifetime_dep$f.4620.2.0 > 1] <- 0
UKB_touchscreen_lifetime_dep$only_one[UKB_touchscreen_lifetime_dep$f.4620.2.0 == 1] <- 1

UKB_touchscreen_lifetime_dep$at_least_two <- NA
UKB_touchscreen_lifetime_dep$at_least_two[UKB_touchscreen_lifetime_dep$f.4620.2.0 == 0 | UKB_touchscreen_lifetime_dep$f.4620.2.0 == 1] <- 0
UKB_touchscreen_lifetime_dep$at_least_two[UKB_touchscreen_lifetime_dep$f.4620.2.0 > 1] <- 1

UKB_touchscreen_lifetime_dep$longest_period_2_weeks <- NA
UKB_touchscreen_lifetime_dep$longest_period_2_weeks[UKB_touchscreen_lifetime_dep$f.4609.2.0 == 0 | UKB_touchscreen_lifetime_dep$f.4609.2.0 == 1] <- 0
UKB_touchscreen_lifetime_dep$longest_period_2_weeks[UKB_touchscreen_lifetime_dep$f.4609.2.0 >= 2] <- 1

UKB_touchscreen_lifetime_dep$GP <- recode(
  UKB_touchscreen_lifetime_dep$f.2090.2.0,
  "No" = 0,
  "Yes" = 1
)

UKB_touchscreen_lifetime_dep$psychiatrist <- recode(
  UKB_touchscreen_lifetime_dep$f.2100.2.0,
  "No" = 0,
  "Yes" = 1
)

## Single episode of probable MD 
#{(1) AND (3) AND (5) AND [(6) OR (7)]} OR {(2) AND (3) AND (5) AND [(6) OR (7)]}
UKB_touchscreen_lifetime_dep$single_episode_MD <- (UKB_touchscreen_lifetime_dep$depressed_week & UKB_touchscreen_lifetime_dep$only_one & UKB_touchscreen_lifetime_dep$longest_period_2_weeks & (UKB_touchscreen_lifetime_dep$GP | UKB_touchscreen_lifetime_dep$psychiatrist) |
                                                     UKB_touchscreen_lifetime_dep$disinterested_week & UKB_touchscreen_lifetime_dep$only_one & UKB_touchscreen_lifetime_dep$longest_period_2_weeks & (UKB_touchscreen_lifetime_dep$GP | UKB_touchscreen_lifetime_dep$psychiatrist))

## Probable Recurrent MD (moderate)
# [(1) OR (2)] AND (4) AND (5) AND (6)
UKB_touchscreen_lifetime_dep$recurrent_MD_moderate <- (UKB_touchscreen_lifetime_dep$depressed_week | UKB_touchscreen_lifetime_dep$disinterested_week) & 
  UKB_touchscreen_lifetime_dep$at_least_two & UKB_touchscreen_lifetime_dep$longest_period_2_weeks & UKB_touchscreen_lifetime_dep$GP

## Probable Recurrent MD (severe)
# [(1) OR (2)] AND (4) AND (5) AND (6)
UKB_touchscreen_lifetime_dep$recurrent_MD_severe <- (UKB_touchscreen_lifetime_dep$depressed_week | UKB_touchscreen_lifetime_dep$disinterested_week) & 
  UKB_touchscreen_lifetime_dep$at_least_two & UKB_touchscreen_lifetime_dep$longest_period_2_weeks & UKB_touchscreen_lifetime_dep$psychiatrist

## Get status of participants with enough information to derive phenotype
UKB_touchscreen_lifetime_dep$eligible <- ifelse((!is.na(UKB_touchscreen_lifetime_dep$depressed_week) &
                                            !is.na(UKB_touchscreen_lifetime_dep$disinterested_week) &
                                            !is.na(UKB_touchscreen_lifetime_dep$GP) &
                                            !is.na(UKB_touchscreen_lifetime_dep$psychiatrist)),1,0)

UKB_touchscreen_lifetime_dep$smith_depression <- 0

UKB_touchscreen_lifetime_dep$smith_depression[UKB_touchscreen_lifetime_dep$single_episode_MD | UKB_touchscreen_lifetime_dep$recurrent_MD_moderate | UKB_touchscreen_lifetime_dep$recurrent_MD_severe] <- 1

## Remove those without enough information to derive phenotype
UKB_touchscreen_lifetime_dep$smith_depression[UKB_touchscreen_lifetime_dep$eligible == 0] <- NA

table(UKB_touchscreen_lifetime_dep$smith_depression)
```


## Get required variables to derived current depressive symptoms - https://pmc.ncbi.nlm.nih.gov/articles/instance/7469862/bin/HBM-41-3922-s001.pdf
```{r}

UKB_touchscreen_current_dep <- UKB_touchscreen %>%
  select(f.eid, f.2050.2.0, f.2060.2.0, f.4526.2.0, 
         f.1930.2.0, f.1960.2.0, f.2050.2.0, f.2060.2.0, f.4526.2.0,
         f.1170.2.0,  f.1200.2.0,
         f.2070.2.0,  f.2080.2.0,
         f.1940.2.0,  f.1950.2.0, f.2020.2.0,  f.2030.2.0) 
```

## Derive current depression phenotypes
```{r derive current depression status}
# Current depression if: depressed mood OR disinterest OR feeling unhappy OR at least one symptom of each of the following: mood, sleep problems, psychomotor or interpersonal

## Define recoding key
reverse_recode_key <- c(
  "Not at all" = "1",
  "Several days" = "2",
  "More than half the days" = "3",
  "Nearly every day" = "4",
  "Do not know" = NA_character_,   # Convert "Do not know" to NA
  "Prefer not to answer" = NA_character_  # Convert "Prefer not to answer" to NA
)

## Depressed mood over the past two weeks for at least more than half of the days - 2050
UKB_touchscreen_current_dep$depressed_mood <- ifelse(recode(UKB_touchscreen_current_dep$f.2050.2.0, !!!reverse_recode_key) > 2, 1, 0)

## Disinterest over the past two weeks for at least more than half of the days - 2060
UKB_touchscreen_current_dep$disinterest <- ifelse(recode(UKB_touchscreen_current_dep$f.2060.2.0, !!!reverse_recode_key) > 2, 1, 0)

## In general feeling very unhappy or extremely unhappy - 4526
UKB_touchscreen_current_dep$unhappy[!is.na(UKB_touchscreen_current_dep$f.4526.2.0)] <- 0
UKB_touchscreen_current_dep$unhappy[UKB_touchscreen_current_dep$f.4526.2.0 == "Prefer not to answer" | UKB_touchscreen_current_dep$f.4526.2.0 == "Do not know "] <- NA
UKB_touchscreen_current_dep$unhappy[UKB_touchscreen_current_dep$f.4526.2.0 == "Very unhappy" | UKB_touchscreen_current_dep$f.4526.2.0 == "Extremely unhappy"] <- 1

## At least one symptom for at least three of four symptom groups related to depression – mood symptoms, sleep problems, psychomotor symptoms or interpersonal symptoms

## Mood symptoms
# Miserable - 1930
UKB_touchscreen_current_dep$mood_miserable <- NA
UKB_touchscreen_current_dep$mood_miserable[UKB_touchscreen_current_dep$f.1930.2.0 == "Yes"] <- 1
UKB_touchscreen_current_dep$mood_miserable[UKB_touchscreen_current_dep$f.1930.2.0 == "No"] <- 0
# Fed-up - 1960
UKB_touchscreen_current_dep$mood_fedup <- NA
UKB_touchscreen_current_dep$mood_fedup[UKB_touchscreen_current_dep$f.1960.2.0 == "Yes"] <- 1
UKB_touchscreen_current_dep$mood_fedup[UKB_touchscreen_current_dep$f.1960.2.0 == "No"] <- 0
# # Depressed mood - 2050
UKB_touchscreen_current_dep$mood_depressed <- ifelse(recode(UKB_touchscreen_current_dep$f.2050.2.0, !!!reverse_recode_key) > 1, 1, 0)
## Disintered mood - 2060
UKB_touchscreen_current_dep$mood_disinterest <- ifelse(recode(UKB_touchscreen_current_dep$f.2060.2.0, !!!reverse_recode_key) > 1, 1, 0)

## Feeling moderately unhappy - 4526
UKB_touchscreen_current_dep$mood_moderately_unhappy[!is.na(UKB_touchscreen_current_dep$f.4526.2.0)] <- 0
UKB_touchscreen_current_dep$mood_moderately_unhappy[UKB_touchscreen_current_dep$f.4526.2.0 == "Prefer not to answer" | UKB_touchscreen_current_dep$f.4526.2.0 == "Do not know "] <- NA
UKB_touchscreen_current_dep$mood_moderately_unhappy[UKB_touchscreen_current_dep$f.4526.2.0  == "Moderately unhappy" | UKB_touchscreen_current_dep$f.4526.2.0 == "Very unhappy" | UKB_touchscreen_current_dep$f.4526.2.0 == "Extremely unhappy"] <- 1
UKB_touchscreen_current_dep$mood_at_least_one <- ifelse((UKB_touchscreen_current_dep$mood_miserable | UKB_touchscreen_current_dep$mood_fedup | UKB_touchscreen_current_dep$mood_depressed | UKB_touchscreen_current_dep$mood_disinterest
                                                        | UKB_touchscreen_current_dep$mood_moderately_unhappy) , 1, 0)

# Sleep problems
# Getting up - 1170
UKB_touchscreen_current_dep$sleep_getting_up <- NA
UKB_touchscreen_current_dep$sleep_getting_up[UKB_touchscreen_current_dep$f.1170.2.0 == "Fairly easy" | UKB_touchscreen_current_dep$f.1170.2.0 == "Very easy"] <- 0
UKB_touchscreen_current_dep$sleep_getting_up[UKB_touchscreen_current_dep$f.1170.2.0 == "Not very easy" | UKB_touchscreen_current_dep$f.1170.2.0 == "Not at all easy"] <- 1
# Insomnia - 1200
UKB_touchscreen_current_dep$sleep_insomnia <- NA
UKB_touchscreen_current_dep$sleep_insomnia[UKB_touchscreen_current_dep$f.1200.2.0 == "Never/rarely" | UKB_touchscreen_current_dep$f.1200.2.0 == "Sometimes"] <- 0
UKB_touchscreen_current_dep$sleep_insomnia[UKB_touchscreen_current_dep$f.1200.2.0 == "Usually"] <- 1
UKB_touchscreen_current_dep$sleep_at_least_one <- ifelse((UKB_touchscreen_current_dep$sleep_getting_up | UKB_touchscreen_current_dep$sleep_insomnia) , 1, 0)

## Psychomotor
# Restlessness - 2070
UKB_touchscreen_current_dep$psychomotor_restlessness <- ifelse(recode(UKB_touchscreen_current_dep$f.2070.2.0, !!!reverse_recode_key) > 2, 1, 0)
# Tiredness - 2080
UKB_touchscreen_current_dep$psychomotor_tiredness <- ifelse(recode(UKB_touchscreen_current_dep$f.2080.2.0, !!!reverse_recode_key) > 3, 1, 0)
UKB_touchscreen_current_dep$psychomotor_at_least_one <- ifelse((UKB_touchscreen_current_dep$psychomotor_restlessness | UKB_touchscreen_current_dep$psychomotor_tiredness) , 1, 0)

## Interpersonal
# irritable - 1940
UKB_touchscreen_current_dep$interpersonal_irritable <- NA
UKB_touchscreen_current_dep$interpersonal_irritable[UKB_touchscreen_current_dep$f.1940.2.0 == "No"] <- 0
UKB_touchscreen_current_dep$interpersonal_irritable[UKB_touchscreen_current_dep$f.1940.2.0 == "Yes"] <- 1
# hurt feelings - 1950
UKB_touchscreen_current_dep$interpersonal_hurt_feelings <- NA
UKB_touchscreen_current_dep$interpersonal_hurt_feelings[UKB_touchscreen_current_dep$f.1950.2.0 == "No"] <- 0
UKB_touchscreen_current_dep$interpersonal_hurt_feelings[UKB_touchscreen_current_dep$f.1950.2.0 == "Yes"] <- 1
# lonliness - 2020
UKB_touchscreen_current_dep$interpersonal_lonely <- NA
UKB_touchscreen_current_dep$interpersonal_lonely[UKB_touchscreen_current_dep$f.2020.2.0 == "No"] <- 0
UKB_touchscreen_current_dep$interpersonal_lonely[UKB_touchscreen_current_dep$f.2020.2.0 == "Yes"] <- 1
# guilt - 2030
UKB_touchscreen_current_dep$interpersonal_guilt <- NA
UKB_touchscreen_current_dep$interpersonal_guilt[UKB_touchscreen_current_dep$f.2030.2.0 == "No"] <- 0
UKB_touchscreen_current_dep$interpersonal_guilt[UKB_touchscreen_current_dep$f.2030.2.0 == "Yes"] <- 1
UKB_touchscreen_current_dep$interpersonal_at_least_one <- ifelse((UKB_touchscreen_current_dep$interpersonal_irritable | UKB_touchscreen_current_dep$interpersonal_hurt_feelings |
                                                                    UKB_touchscreen_current_dep$interpersonal_lonely | UKB_touchscreen_current_dep$interpersonal_guilt) , 1, 0)

## Get status of participants with enough information to derive phenotype
UKB_touchscreen_current_dep$eligible <- ifelse(!is.na(UKB_touchscreen_current_dep$depressed_mood) & !is.na(UKB_touchscreen_current_dep$disinterest) & !is.na(UKB_touchscreen_current_dep$unhappy) &
                                                 !is.na(UKB_touchscreen_current_dep$mood_at_least_one) & !is.na(UKB_touchscreen_current_dep$sleep_at_least_one) & 
                                                 !is.na(UKB_touchscreen_current_dep$psychomotor_at_least_one) & !is.na(UKB_touchscreen_current_dep$interpersonal_at_least_one), 1, 0)

UKB_touchscreen_current_dep$current_depression <- 0

UKB_touchscreen_current_dep$current_depression[UKB_touchscreen_current_dep$depressed_mood | UKB_touchscreen_current_dep$disinterest | UKB_touchscreen_current_dep$unhappy |
                                                 ((UKB_touchscreen_current_dep$mood_at_least_one + UKB_touchscreen_current_dep$sleep_at_least_one +
                                                     UKB_touchscreen_current_dep$psychomotor_at_least_one + UKB_touchscreen_current_dep$interpersonal_at_least_one) > 2)] <- 1

## Remove those without enough information to derive phenotype
UKB_touchscreen_current_dep$current_depression[UKB_touchscreen_current_dep$eligible == 0] <- NA

table(UKB_touchscreen_current_dep$current_depression)
```


## Get those with current depression according to Smith et al criteria and current symptoms

```{r combine depression phenotypes}
UKB_touchscreen_depression <- left_join(UKB_touchscreen_current_dep, UKB_touchscreen_lifetime_dep, by = "f.eid")
UKB_touchscreen_depression$depression <- NA
UKB_touchscreen_depression$depression[UKB_touchscreen_depression$smith_depression & UKB_touchscreen_depression$current_depression] <- 1
UKB_touchscreen_depression$depression[UKB_touchscreen_depression$smith_depression & UKB_touchscreen_depression$current_depression == 0] <- 0
UKB_touchscreen_depression$depression[UKB_touchscreen_depression$smith_depression == 0 & UKB_touchscreen_depression$current_depression == 0] <- 0
UKB_touchscreen_depression$depression[UKB_touchscreen_depression$smith_depression == 0 & UKB_touchscreen_depression$current_depression == 1] <- 0

UKB_touchscreen_depression$depression_sensitivity <- UKB_touchscreen_depression$depression
UKB_touchscreen_depression$depression_sensitivity[UKB_touchscreen_depression$smith_depression == 0 & UKB_touchscreen_depression$current_depression == 1] <- NA

table(UKB_touchscreen_depression$depression)
table(UKB_touchscreen_depression$depression_sensitivity)

```


## Save current depression phenotyp

```{r save}

write.csv(UKB_touchscreen_depression, "/resources/UKB_current_depression_imaging.csv", row.names = FALSE)
```


<!-- ## Recode depression symptom variables -->
<!-- Current depression phenotype at imaging based on: https://onlinelibrary.wiley.com/doi/10.1002/hbm.25690 -->
<!-- f.2050.2.0 - Frequency of depressed mood in last 2 weeks -->
<!-- f.2060.2.0 - Frequency of unenthusiasm/disinterest in last 2 weeks -->
<!-- f.2070.2.0 - Frequency of tenseness/restlessness in last 2 weeks -->
<!-- f.2080.2.0 - Frequency of tiredness/lethargy in last 2 weeks. -->
<!-- ```{r recode variables} -->
<!-- ## Define recoding key -->
<!-- reverse_recode_key <- c( -->
<!--   "Not at all" = "1", -->
<!--   "Several days" = "2", -->
<!--   "More than half the days" = "3", -->
<!--   "Nearly every day" = "4", -->
<!--   "Do not know" = NA_character_,   # Convert "Do not know" to NA -->
<!--   "Prefer not to answer" = NA_character_  # Convert "Prefer not to answer" to NA -->
<!-- ) -->

<!-- ## Apply recoding and remove rows with NAs -->
<!-- UKB_RDS_4 <- UKB_touchscreen %>% -->
<!--   select(f.eid, f.2050.2.0, f.2060.2.0, f.2070.2.0, f.2080.2.0) %>% -->
<!--   mutate(across(-f.eid, ~ recode(., !!!reverse_recode_key))) %>% -->
<!--   mutate(across(-f.eid, as.numeric)) %>%  ## Convert to numeric -->
<!--   mutate(current_depression = rowSums(across(-f.eid))) ## Participant without complete data not summed -->

<!-- ``` -->

